% Document class and font size
\documentclass[letter,9pt]{extarticle}

% Packages
\usepackage[utf8]{inputenc} % For input encoding
\usepackage{geometry} % For page margins
\geometry{a4paper, margin=0.6in} % Set paper size and margins
\usepackage{titlesec} % For section title formatting
\usepackage{enumitem} % For itemized list formatting
\usepackage{hyperref} % For hyperlinks
\usepackage{xcolor}

% Formatting
\setlist{noitemsep} % Removes item separation
\titleformat{\section}{\large\bfseries}{\thesection}{1em}{}[\titlerule] % Section title format
\titlespacing*{\section}{0pt}{\baselineskip}{\baselineskip} % Section title spacing

\definecolor{blueBeamer}{rgb}{0.1484 ,   0.3945  ,  0.9727}
\hypersetup{
     colorlinks   = true,
     citecolor    = blueBeamer,
     citebordercolor =. ,
     linkcolor   = blueBeamer,
     linkbordercolor =. ,
     urlcolor = blueBeamer,
     urlbordercolor =.
}

% Begin document
\begin{document}

% Disable page numbers
\pagestyle{empty}



% Header
\begin{center}
{\Large \textbf{Felipe Arteaga}}\\[2pt] % Name
\textit{March 2024 UC Berkeley Economics Ph.D. graduate seeking roles in Economics \& Data Science}\\[3pt]
Berkeley, CA | \href{mailto:fharteaga@berkeley.edu}{fharteaga@berkeley.edu} | +1 (510) 365-9707 | \href{https://fharteaga.github.io/}{fharteaga.github.io} 
\end{center}

% Experience Section
\section*{EXPERIENCE}
\noindent
\textbf{ConsiliumBots} -- \textit{Research Affiliate}  \hfill New York, NY $|$ May 2019 - Present % Company name 
\begin{itemize}
    \item Led the development and launch of smart, personalized notification systems on school choice platforms across 5 Latin American countries (Brazil, Chile, Colombia, Ecuador, and Peru), significantly enhancing student placement outcomes.  % Job responsibilities and achievements
\end{itemize}
\noindent
\textbf{University of California, Berkeley} -- \textit{Teaching assistant} \hfill Berkeley, CA $|$ August 2019 - Present
\begin{itemize}
    \item Courses: MBA Data Analytics (Causal inference and machine learning), Honors Intermediate Microeconomics. Health Economics, Intermediate Microeconomics.  % Job responsibilities and achievements
\end{itemize}
\noindent
\textbf{Ministry of Education} -- \textit{Lead researcher}  \hfill Santiago, Chile $|$ March 2015 - July 2018 % Company name and location
\begin{itemize}
    \item Served as part of the core team that spearheaded the design, rollout, and evaluation of the new countrywide centralized school choice process that assigns 87\% of all the seats in the Chilean education system. % Job responsibilities and achievements
\end{itemize}
\noindent
\textbf{Abdul Latif Jameel Poverty Action Lab (J-PAL)} -- \textit{Research Associate}\hfill Santiago, Chile $|$ March 2013 - July 2018 % Company name and location \hfill  % Position and duration
\begin{itemize}
    \item Led research efforts for high-impact education projects across Chile, Peru, the Dominican Republic, and the USA. Supported Economic professors Francisco Gallego (PUC) and Christopher Neilson (Yale).
\end{itemize}

% Additional Experience or Volunteer Work


% Projects Section
\section*{PROJECTS}

\noindent
\textbf{Predicting risky school choice applicants} \hfill   2017 – Ongoing 
\begin{itemize}
    \item Designed an algorithm that predicts placement probabilities to classify students with a considerable placement risk.
    \item Led the implementation of an API for live risk classification in five countries, impacting over 2 million applicants.
    \item Evaluated the causal effect of the warnings for high-risk applicants for \href{https://academic.oup.com/qje/article/137/3/1791/6544686?login=false}{Chile and New Haven, CT}, and  \href{https://publications.iadb.org/en/can-information-school-attributes-and-placement-probabilities-direct-search-and-choice-evidence}{Ecuador and Peru}.
\end{itemize}
\noindent
\textbf{Role of information for school applications} \hfill Chile, Perú, Ecuador $|$ 2020-2022
\begin{itemize}
    \item Collaborated on the design of personalized report cards with information about options for school applicants.
    \item Contributed to the implementation in Chile, Perú, and Ecuador, reaching 90\%+ of school applicants.
    \item Evaluated the causal effect of giving information to applicants using A/B testing, published as a \href{https://publications.iadb.org/en/can-information-school-attributes-and-placement-probabilities-direct-search-and-choice-evidence}{IDB working paper}.
\end{itemize}

\noindent
\textbf{Nationwide school application platform} \hfill Chile $|$ 2015 – 2018
\begin{itemize}
    \item Collaborated on the design of a matching algorithm for centralized admission to the Chilean PK-12th education system.
    \item Participated in the gradual implementation of the platform covering from 1\% to 100\% of school admissions in 4 years.
    \item Since 2019, this system has assigned to schools over 600.000 applicants yearly, respecting families' preferences.
\end{itemize}


% Education Section
\section*{EDUCATION}
\textbf{University of California, Berkeley}, Berkeley, CA \hfill  Expected: March 2024\\ % University name and location
\textit{Ph.D. in Economics. Fields: Labor economics and Industrial Organization}\vspace{.1cm}\\ % Degree and GPA
\textbf{Pontificia Universidad Católica}, Santiago, Chile \hfill  December 2013\\ % University name and location
\textit{M.S. in Engineering}\vspace{.1cm}\\   % Degree and GPA
\textbf{Pontificia Universidad Católica}, Santiago, Chile \hfill  December 2012\\ % University name and location
\textit{B.S. in Industrial Engineering}\vspace{.1cm}\\   % Degree and GPA
\textbf{University of British Columbia}, Vancouver, Canada \hfill  January 2011\\ % University name and location
\textit{Exchange student}   % Degree and GPA

% Skills Section
\section*{SKILLS}
\begin{itemize}
    \item \textbf{Programming:} Matlab, Stata, Python, R, Java, SQL.
    \item \textbf{Statistics \& Methods:} Causal inference (RCT, IV, DiD, RDD), structural modeling (demand estimation), prediction  (supervised and unsupervised machine learning methods)
\end{itemize}

\section*{RESEARCH PAPERS}

\noindent
\textbf{Published}
\begin{itemize}
    \item ``\href{https://academic.oup.com/qje/article/137/3/1791/6544686?login=false}{Smart Matching Platforms and Heterogeneous Beliefs in Centralized School Choice}'' (w/ Adam Kapor, Christopher Neilson, and Seth Zimmerman. \textit{Quarterly Journal of Economics}, 2022)    \end{itemize}
\noindent
\textbf{Working papers} 
\begin{itemize}
    \item ``\href{https://fharteaga.github.io/pdfs/arteagaJMP.pdf}{Imperfect Information and Outside Options in Centralized School Choice}''  (Job Market Paper)
    \item ``\href{https://publications.iadb.org/en/can-information-school-attributes-and-placement-probabilities-direct-search-and-choice-evidence}{Can Information on School Attributes and Placement Probabilities Direct Search and Choice? Evidence from Choice Platforms in Ecuador and Perú}'' (w/ G. Elaqua, T. Krussig, C. Méndez, and C. Neilson. \textit{IDB WP} 2022)
    %\item ``School Segregation in Chile: Residence, co-payment, or preferences?'' (w/ Valentina Paredes and Ricardo Paredes)
\end{itemize}



% End document
\end{document}
